Regime transition identification for water utilization of river basin

### 2020-10-29 tex/main/manuscript.tex
change configuration to allocation, priority to provision

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		\item Social development is usually accompanied by a change of priority in water use towards social and economic systems because of higher returns:
		$$ Dev. \propto P $$
		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
		\item Social development usually lead to more complex structure in configuration of water resources, which is a result of division and cooperation between regions and sectors for developing:
		$$ Dev \propto C $$ 
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item Further social development can only be achieved by effectively alleviating the water resource stresses generated in the process of development through technological means:
		$$ Dev \propto S^{-1} $$
	\end{itemize}

	% 将三者合一起，即：
	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with social development: 
	$$ Dev. \propto P*C*S^{-1} $$

@@

	$$ Dev. \propto ln(I_P) + ln(I_C) - ln(I_S) $$

@@

	$$ IWRU = I'_T + I'_P - I'_S $$

>>>>

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		\item Social development is usually accompanied by a change of priority in water use towards social and economic systems because of higher returns:
		$$ Dev. \propto P $$
		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
		\item Social development usually lead to more complex structure in configuration of water resources, which is a result of division and cooperation between regions and sectors for developing:
		$$ Dev \propto A $$ 
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item Further social development can only be achieved by effectively alleviating the water resource stresses generated in the process of development through technological means:
		$$ Dev \propto S^{-1} $$
	\end{itemize}

	% 将三者合一起，即：
	We combine the above three dimensions for an integrated index, remaining their positive or negative relationship with social development: 
	$$ Dev. \propto P*A*S^{-1} $$

@@

	$$ Dev. \propto ln(I_P) + ln(I_A) - ln(I_S) $$

@@

	$$ IWRU = I'_A + I'_P - I'_S $$
